A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2014-05-22 cikm_paper/paper.tex
kleinere bibliography
bibliography opgeschoond
proceedings of the fourth conference -> proc 4th conf

\documentclass{sig-alternate-2013}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{document}

@@

\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case

@@

Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule\endhead

>>>>

\documentclass{sig-alternate}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{document}

@@

{\small\bibliography{Bibliography}}  % sigproc.bib is the name of the Bibliography in this case

@@

Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WN & IWN & NWN \\ \midrule\endhead
